Precise predictions for same-sign W-bosons scattering at the LHC

### 2018-01-26 Draft/abstract.tex
series of imporvements, corrections from the beginning up to section 3.3

In this article, a detailed study of the vector-boson scattering for two positively charged W bosons is presented.
In particular, a comparison between the full next-to-leading (NLO) QCD corrections against several approximations is carried out.
This study is not only performed in the usual fiducial region used by experimental collaborations but also in a more inclusive set-up.
This allows to infer precisely the quality of such approximations.
Finally, NLO predictions matched to various parton shower are discussed.
This study allows thus to infer the systematic errors related to vector-boson scattering at the NLO-QCD level and beyond.

>>>>

In this article, a detailed study of the vector-boson scattering for two positively charged W bosons is presented.
In particular, a comparison between the full next-to-leading (NLO) QCD corrections against several approximations is carried out.
This study is not only performed in the usual fiducial region used by experimental collaborations but also in a more inclusive set-up.
This allows to infer precisely the quality of such approximations.
Finally, NLO predictions matched to various parton shower are also discussed.
Thanks to this, it is thus possible to infer the systematic errors related to vector-boson scattering at the NLO-QCD level and beyond.

### 2018-01-26 Draft/definition.tex
series of imporvements, corrections from the beginning up to section 3.3

This process possesses three LO contributions of different orders.
The first one is of order $\mathcal{O}{\left(\alpha^{6}\right)}$ is referred to as EW contributions.
In addition to typical VBS contributions as shown on the left of Fig.~\ref{diag:LO}, it also features $s$-channel contributions.
These types of contributions will play a particular role in the study of the various contributions in Section \ref{subsec:contributions}.
Some of them take the form of decay chains as for example the diagram represented in the middle of Fig.~\ref{diag:LO} while others are tri-boson contributions (right of Fig.~\ref{diag:LO}).
The VBS diagrams typically dominate the full process.
But all these contributions form a single gauge-invariant set of contributions and therefore cannot be separated.

@@

Usually, in experimental measurements, special VBS-cuts are designed in order to enhance the EW contribution over the QCD one.
These cuts are based on the fact that the two contributions have rather different kinematic.
The EW contribution is characterised by two jets with large rapidity in the peripheral region as well as a large invariant mass.
The two W bosons are mostly produced centrally.
This is in opposition with the QCD component which favours jets in the central region.
Therefore, the event selection usually involves rapidity-difference and invariance mass cuts for the jets.
This will also be discussed in Section \ref{subsec:contributions}.

>>>>

This process possesses three LO contributions of different orders.
The first one is of order $\mathcal{O}{\left(\alpha^{6}\right)}$ and is referred to as EW contributions.
In addition to typical VBS contributions as shown on the left of Fig.~\ref{diag:LO}, it also features $s$-channel contributions.
These types of contributions will play a particular role in the study of the various contributions in Section \ref{subsec:contributions}.
Some of them take the form of decay chains as for example the diagram represented in the middle of Fig.~\ref{diag:LO} while others are tri-boson contributions (right of Fig.~\ref{diag:LO}).
The VBS diagrams typically dominate the full process.
But all these contributions form a single gauge-invariant set of contributions and therefore cannot be separated.

@@

Usually, in experimental measurements, special VBS-cuts are designed in order to enhance the EW contribution over the QCD one.
These cuts are based on the fact that the two contributions have rather different kinematic.
The EW contribution is characterised by two jets with large rapidity in the peripheral region as well as a large invariant mass.
The two W bosons are mostly produced centrally.
This is in opposition with the QCD component which favours jets in the central region.
Therefore, the event selection usually involves rapidity-difference and invariance-mass cuts for the jets.
This will also be discussed in Section \ref{subsec:contributions}.

### 2018-01-26 Draft/description.tex
series of imporvements, corrections from the beginning up to section 3.3

  \item {{\sc{Phantom}}~\cite{Ballestrero:2007xq} is a dedicated tree--level Monte Carlo for six parton final states at $pp,\, p\bar{p}$
  and $e^+e^-$ colliders at $\alpha^6$ and $\alpha^4\alphas^2$ including interferences between the two sets of diagrams.
It employs complete tree--level matrix elements in the complex--mass scheme~\cite{Denner:2006ic} computed via the modular helicity
formalism~\cite{Ballestrero:1999md,Ballestrero:1994jn}. The integration uses a multichannel approach~\cite{BERENDS1985441} and an adaptive
strategy~\cite{PETERLEPAGE1978192}. {\sc{Phantom}} generates unweighted events at parton--level for both the SM and a few instances of BSM theories.}

@@

  \item The program {\sc MoCaNLO+Recola} is made of a flexible Monte Carlo program dubbed {\sc MoCaNLO}~\cite{MoCaNLO} and the general matrix element generator {\sc Recola} \cite{Actis:2012qn,Actis:2016mpe}.
To numerically evaluate the one-loop scalar and tensor integrals, {\sc Recola} relies on the {\sc Collier} library \cite{Denner:2014gla,Denner:2016kdg},
These tools have been successfully used for the computation of NLO corrections for VBS~\cite{Biedermann:2016yds,Biedermann:2017bss}.

>>>>

  \item {\sc Phantom}~\cite{Ballestrero:2007xq} is a dedicated tree-level Monte Carlo for six parton final states at $\Pp \Pp,\, \Pp\bar{\Pp}$
  and $\Pe^+\Pe^-$ colliders at orders $\alpha^6$ and $\alpha^4\alphas^2$ including interferences between the two sets of diagrams.
It employs complete tree-level matrix elements in the complex-mass scheme~\cite{Denner:2006ic} computed via the modular helicity
formalism~\cite{Ballestrero:1999md,Ballestrero:1994jn}. The integration uses a multichannel approach~\cite{Berends:1984gf} and an adaptive
strategy~\cite{Lepage:1977sw}. {\sc Phantom} generates unweighted events at parton level for both the SM and a few instances of BSM theories.

@@

\item The program {\sc MoCaNLO+Recola} is made of a flexible Monte Carlo program dubbed {\sc MoCaNLO}~\cite{MoCaNLO} and of the general matrix element generator {\sc Recola}~\cite{Actis:2012qn,Actis:2016mpe}.
The fast integration is ensured by using similar phase-space mappings to those of Refs.~\cite{Berends:1994pv,Denner:1999gp,Dittmaier:2002ap}.
The IR divergences appearing in the real corrections are handles with the help of the Cantani--Seymour dipole formalism \cite{Catani:1996vz,Dittmaier:1999mb}.
To numerically evaluate the one-loop scalar and tensor integrals, {\sc Recola} relies on the {\sc Collier} library \cite{Denner:2014gla,Denner:2016kdg}.
These tools have been successfully used for the computation of NLO corrections for high-multiplicity processes and in particlar VBS~\cite{Biedermann:2016yds,Biedermann:2017bss}.

### 2018-01-26 Draft/process.tex
series of imporvements, corrections from the beginning up to section 3.3

A further refinement is to consider the full real contributions as well as part of the virtual \MP{I cannot remember exactly what is included}.
This assumes a cancellation of infrared poles.
Such predictions are provided by {\sc MG5\_aMC}.

Finally the full computation implies to also consider EW corrections in the virtual as well as real corrections \cite{Biedermann:2017bss}.
Such full predictions are provided by the combination {\sc MoCaNLO+Recola} as published in Ref.~\cite{Biedermann:2017bss}.

>>>>

A further refinement is to consider the full real contributions as well as part of the virtual.
In particular one can consider only one-loop amplitudes where there is no gluon exchange between the quarks and assuming a cancellation of the infrared (IR) poles. \MP{True? I cannot remember exactly what is included}.
Such predictions are provided by {\sc MG5\_aMC}.

Finally the full $\mathcal{O}{\left(\alphas \alpha^{6}\right)}$ computation consists also of EW corrections in the virtual as well as real corrections \cite{Biedermann:2017bss}.
Such predictions are provided by the combination {\sc MoCaNLO+Recola} as published in Ref.~\cite{Biedermann:2017bss}.
